Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-25 main.tex
improved author formatting.

\author{
\IEEEauthorblockN{Jan Ciesko}
\IEEEauthorblockA{\textit{Computer Science Reseach Institute} \\
\textit{Sandia National Laboratories}\\
Albuquerque, NM, USA\\
jciesko@sandia.gov}
\and
\IEEEauthorblockN{David Poliakoff}
\IEEEauthorblockA{\textit{Computer Science Reseach Institute} \\
\textit{Sandia National Laboratories}\\
Albuquerque, NM, USA\\
dzpolia@sandia.gov}
\and
\IEEEauthorblockN{David S. Hollman}
\IEEEauthorblockA{\textit{Computer Science Reseach Institute} \\
\textit{Sandia National Laboratories}\\
Livermore, CA, USA\\
dshallm@sandia.gov}
\and
\IEEEauthorblockN{Christian C. Trott}
\IEEEauthorblockA{\textit{Computer Science Reseach Institute} \\
\textit{Sandia National Laboratories}\\
Albuquerque, NM, USA\\
ctrott@sandia.gov}
\and
\IEEEauthorblockN{Damien Lebrun-Grandié}
\IEEEauthorblockA{\textit{Computational Sciences and Engineering} \\
\textit{Oak Ridge National Laboratory}\\
Oak Ridge, TN, USA\\
lebrungrandt@ornl.gov}
}

>>>>

\author{
\IEEEauthorblockN{Jan Ciesko}
\IEEEauthorblockA{\textit{Computer Science Reseach Institute} \\
\textit{Sandia National Laboratories}\\
Albuquerque, NM, USA\\
jciesko@sandia.gov}
\and
\IEEEauthorblockN{David Poliakoff}
\IEEEauthorblockA{\textit{Computer Science Reseach Institute} \\
\textit{Sandia National Laboratories}\\
Albuquerque, NM, USA\\
dzpolia@sandia.gov}
\and
\IEEEauthorblockN{David S. Hollman}
\IEEEauthorblockA{\textit{Computer Science Reseach Institute}\\
\textit{Sandia National Laboratories}\\
Livermore, CA, USA\\
dshallm@sandia.gov}
\and
\IEEEauthorblockN{
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ Christian C. Trott }
\IEEEauthorblockA{
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \textit{Computer Science Reseach Institute} \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \textit{Sandia National Laboratories}\\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  Albuquerque, NM, USA\\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ ctrott@sandia.gov}
\and
\IEEEauthorblockN{ Damien Lebrun-Grandié\ \ \ \ \ \ \ \ \ \ \ }
\IEEEauthorblockA{\textit{Computational Sciences and Engineering}\ \ \ \ \ \ \ \ \ \ \ \\
\textit{Oak Ridge National Laboratory}\ \ \ \ \ \ \ \ \ \ \ \\
Oak Ridge, TN, USA\ \ \ \ \ \ \ \ \ \ \ \\
lebrungrandt@ornl.gov\ \ \ \ \ \ \ \ \ \ \ }
}
